Using occupancy theory and Bayesian models to estimate otter populations in southeastern Minnesota

### 2010-03-04 Presentation.tex
Last revisions?

\section{Discussion}
\begin{frame}{Obtaining convergence on the data}
	\begin{itemize}
		\item All of 2003 data converged with standard model
		\item None of 2004 data converged with standard model
		\begin{itemize}
			\item Removed false detection. 2004 data with 402m plot size
			converged, but estimates not dependable
		\end{itemize}
		\item CAR model never converged with $E$. Without $E$, poor
		estimates for $\psi$
	\end{itemize}
\end{frame}

\begin{frame}{Summary and interpretation of estimates}
	\begin{center}
		\includegraphics[width=10cm]{Figures/Graphs/2003Psi.pdf}
	\end{center}
\end{frame}

\begin{frame}{Summary and interpretation of estimates}
	\begin{itemize}
		\item Estimates for all parameters increase with plot size
		\item Possible hypotheses:
		\begin{itemize}
			\item \(\psi\) and \(\theta\)
			\item \(p\) and \(E\)
		\end{itemize}
		\item Used data from all plots, not alternating plots
		\begin{itemize}
			\item More data more useful than more independence
		\end{itemize}
	\end{itemize}
	\begin{center}
		\includegraphics[width=10cm]{Figures/Diagrams/Aggregation.pdf}
	\end{center}
\end{frame}

>>>>

\section{Discussion}

\begin{frame}{Obtaining convergence on the data}
	\begin{itemize}
		\item Occupancy data from the winters of 2003 and 2004
		\item 2003 data set consists mostly of multiple observers flying on
		multiple days after each snow event
		\item 2004 data set consists mostly of one observer flying on one day
		after each snow event
	\end{itemize}
\end{frame}

\begin{frame}{Obtaining convergence on the data}
	\begin{itemize}
		\item All of 2003 data converged with standard model
		\item None of 2004 data converged with standard model
		\begin{itemize}
			\item Removed false detection. 2004 data with 402m plot size
			converged, but estimates not dependable
		\end{itemize}
		\item CAR model never converged with $E$. Without $E$, poor
		estimates for $\psi$
	\end{itemize}
\end{frame}

\begin{frame}{Summary of estimates}
	\begin{center}
		\includegraphics[width=8cm]{Figures/R/MissResults.pdf}
	\end{center}
\end{frame}

\begin{frame}{Summary of estimates}
	\begin{center}
		\includegraphics[width=10cm]{Figures/Graphs/2003Psi.pdf}
	\end{center}
\end{frame}

\begin{frame}{Interpretation of estimates}
	\begin{itemize}
		\item Estimates for all parameters increase with plot size
		\item Possible hypotheses:
		\begin{itemize}
			\item \(\psi\) and \(\theta\)
			\item \(p\) and \(E\)
		\end{itemize}
		\item Used data from all plots, not alternating plots
		\begin{itemize}
			\item More data more useful than less dependence
		\end{itemize}
	\end{itemize}
	\begin{center}
		\includegraphics[width=10cm]{Figures/Diagrams/Aggregation.pdf}
	\end{center}
\end{frame}
